---
title: "09_combining_annotations_full_annotation"
author: "Anna Steinberg"
date: "`r Sys.Date()`"
output: distill::distill_article
---

# Goal of the script: Create full annotation dataset 

Combine non-expert, expert annotations and expert discussion into one dataset and compute final values, units and pages. For each type (value, unit, page) the procedure is rather complex, so for each type the final entry is first computed using complex if-conditions, then every condition is checked manually and issues are resolved manually. 
The resulting full annotations dataframe is used to create the gold standard and the annotation dataset. To combine the datasets back together a merge id is created. 

# Load libraries
```{r}
library(tidyverse)
library(readxl)
```

```{r}
source("../pivot.R")
```

# Merge all datasets together

## Load non_expert annotations
```{r}
load_non_expert_annotations <- function(cleaned_data, pivot_vars) {
  # Pivot the data with the requested variables
  pivot <- pivot_w_split(cleaned_data, pivot_vars)

  # Create agreement for value_correct and unit_correct to identify rows where non-expert annotators disagreed
  agreement_vars <- c("value_correct", "unit_correct")
  for (var in agreement_vars) {
    pivot <- agreement_func(pivot, var)
  }
  pivot <- pivot %>% mutate(agreement_value_and_unit = ifelse(agreement_value_correct == T & agreement_unit_correct == T,T,F))

  # Recreate variables used for identifying reports for expert review
  pivot <- pivot %>%
    mutate(document_expert_requested_by_at_least_one_annotator = ifelse(rowSums(select(., contains("document_expert_needed")) == "Yes", na.rm = TRUE) > 0, "Yes", "No"))
  
  pivot <- pivot %>%
    mutate(row_expert_requested_by_at_least_one_annotator_or_disagreement = ifelse(rowSums(select(., contains("record_expert_needed")) == "Yes", na.rm = TRUE) > 0 | agreement_value_and_unit == F, "Yes", "No"))
  
  return(pivot)
}
```

```{r}
cleaned_data <- read.csv("../../data/processed/non_expert_annotations/non_expert_annotations_cleaned.csv")

# Choose all variables from non-expert annotations we want to include in final annotations
pivot_vars <- c("value_correct", "corrected_value", "unit_correct", "corrected_unit", "page_correct", "corrected_page", "comment", "record_expert_needed", "document_comment", "document_expert_needed", "metric_name", "reporting_type")

non_expert_annotations <- load_non_expert_annotations(cleaned_data, pivot_vars)
```

Delete agreement variables because they will be recomputed later
```{r}
non_expert_annotations <- non_expert_annotations %>% 
  select(-starts_with("agreement"))
```

Compute value chosen by non-experts (needed for mismatch computation below)
```{r}
non_expert_annotations <- non_expert_annotations %>% 
  mutate(
    value_1 = ifelse(value_correct_1 == "Yes", llm_value, corrected_value_1),
    value_2 = ifelse(value_correct_2 == "Yes", llm_value, corrected_value_2),
  )
```

## Add expert annotations to this dataframe
```{r}
expert_annotations <- read.csv("../../data/processed/expert_discussion/expert_disagreement.csv")
```

Remove agreement variables and true variables (value, unit and page)
```{r}
expert_annotations <- expert_annotations %>% 
  # will be recomputed
  select(-starts_with("agreement"), -starts_with("true")) %>%
  
  # error in previous dataset, supposed to be character all along
  mutate(Corrected.page.Ann.2 = as.character(Corrected.page.Ann.2)) %>% 
  mutate(Page.corrected..fill.in.if.necessary..g1 = as.character(Page.corrected..fill.in.if.necessary..g1)) #%>% 
  
  # only select columns for merging and columns which are new in expert_annotations compared to non_expert annotations
  #select(Report.Name, ID, Page.used, LLM.Year, LLM.Scope, LLM.Value, LLM.Unit,  ends_with("g1"), ends_with("g2"), row_disagreement_value_unit_page_or_unclear)
```

Create identifier for reports passed to expert annotations
```{r}
reports_in_expert_annotations <- expert_annotations %>% select(Report.Name) %>% distinct()
```

Join non-expert and expert annotations
```{r}
annotations <- left_join(non_expert_annotations, expert_annotations, by = c(
  "report_name" = "Report.Name",
  "ID",
  "page_used" = "Page.used",
  "llm_year" = "LLM.Year",
  "llm_scope" = "LLM.Scope",
  "llm_value" = "LLM.Value",
  "llm_unit" = "LLM.Unit"
  ))
```

### Solve mismatch
In the expert annotations the columns of the non-experts are sometimes switched compared to the non-expert annotations. We need to resolve this by 
1) identifying the reports which are concerned
2) swapping the columns in those reports

1) Identify reports with mismatch
```{r}
mismatch <- annotations %>% filter(report_name %in% reports_in_expert_annotations$Report.Name) %>% 
  filter(
    (is.na(value_1) & !is.na(Value.Ann.1)) |
       (!is.na(value_1) & is.na(Value.Ann.1)) |
      value_1 != Value.Ann.1 ) %>%
  select(report_name, ID, value_1, value_2, Value.Ann.1, Value.Ann.2)

mismatch %>% distinct(report_name)
```

2) Swapping the columns in those reports
Concerned columns:
- value_correct_1/2
- corrected_value_1/2
- unit_correct_1/2
- corrected_unit_1/2
- page_correct_1/2
- corrected_page_1/2
- comment_1/2
- document_comment_1/2
- record_expert_needed_1/2
- document_expert_need_1/2
- metric_name_1/2
- reporting_type_1/2

We want to change the columns from the non-expert annotations with the help of the columns from the expert annotations.
We use value_1 and value_2 (non-expert annotations) and Value.Ann.1 and Value.Ann.2 (expert annotations) to do the swap.
For correct swapping, we need to create temporary variables which we delete after the swap

```{r}
swap_values <- function(data, mismatch, non_expert_val, non_expert_check_val, expert_check_val) {
  non_expert_val1 <- sym(paste0(non_expert_val, "_1"))
  non_expert_val_temp <- sym(paste0(non_expert_val, "_1_temp"))  # Create symbol for temporary variable
  non_expert_val2 <- sym(paste0(non_expert_val, "_2"))  # Convert variable name to symbol
  non_expert_check_val1 <- sym(paste0(non_expert_check_val, "_1"))  # Convert variable name to symbol
  non_expert_check_val2 <- sym(paste0(non_expert_check_val, "_2"))  # Convert variable name to symbol
  expert_check_val1 <- sym(paste0(expert_check_val, ".1")) # Convert variable name to symbol)
  expert_check_val2 <- sym(paste0(expert_check_val, ".2")) # Convert variable name to symbol)
  
  data <- data %>%
    mutate(!!non_expert_val_temp := case_when(
      report_name %in% mismatch$report_name & (is.na(!!non_expert_check_val2) & is.na(!!expert_check_val1)) ~ !!non_expert_val2,
      report_name %in% mismatch$report_name & !!non_expert_check_val2 == !!expert_check_val1 ~ !!non_expert_val2, 
      TRUE ~ !!non_expert_val1
    )) %>%
    mutate(!!non_expert_val2 := case_when(
      report_name %in% mismatch$report_name & (is.na(!!non_expert_check_val1) & is.na(!!expert_check_val2)) ~ !!non_expert_val1,
      report_name %in% mismatch$report_name & !!non_expert_check_val1 == !!expert_check_val2 ~ !!non_expert_val1,
      TRUE ~ !!non_expert_val2
    ),
    !!non_expert_val1 := !!non_expert_val_temp
    ) %>%
    select(-!!non_expert_val_temp)  # Remove the temporary column
    
  return(data)
}

# The function does the following
# Example for swapping value_correct_1/2
#data <- data %>% mutate(
# value_correct_1_temp = case_when(
#     report_name %in% mismatch$report_name & (is.na(value_2) & is.na(Value.Ann.1)) ~ value_correct_2,
#     report_name %in% mismatch$report_name & value_2 == Value.Ann.1 ~ value_correct_2, 
#     .default = value_correct_1
#   ),
#    value_correct_2 = case_when(
#     report_name %in% mismatch$report_name & (is.na(value_1) & is.na(Value.Ann.2)) ~ value_correct_1,
#     report_name %in% mismatch$report_name & value_1 == Value.Ann.2 ~ value_correct_1,
#      .default = value_correct_2
#    ),
#    value_correct_1 = value_correct_1_temp
#)
```

```{r}
concerned_variables <- c("value_correct", "corrected_value", "unit_correct", "corrected_unit", "page_correct", "corrected_page", "comment", "record_expert_needed", "document_comment", "document_expert_needed", "metric_name", "reporting_type")

for (var in concerned_variables) {
  annotations <- swap_values(annotations, mismatch, var, "value", "Value.Ann")
}
```

Check if the swap was successful
```{r}
#annotations %>% filter(report_name %in% mismatch$report_name) %>% select(report_name, ID, value_1, value_2, Value.Ann.1, Value.Ann.2)
```

More checks. If it worked we expect 0 observations here.
```{r}
annotations %>% filter(value_correct_1 != Value.correct..Yes.No..Ann.1) %>% select(report_name, value_correct_1, corrected_value_1, Value.correct..Yes.No..Ann.2, Value.corrected.Ann.2, Value.correct..Yes.No..Ann.1, Value.corrected.Ann.1, value_correct_2, corrected_value_2)
```
```{r}
annotations %>% filter(value_correct_2 != Value.correct..Yes.No..Ann.2)
```
### Remove duplicate columns
```{r}
annotations <- annotations %>% select(
  -value_1, -value_2, -Value.Ann.1, -Value.Ann.2,
  -Document.comment.Annotator.1, -Document.comment.Annotator.2,
  -Document.level.expert.adjudication.requested.by.at.least.1.annotator,
  -row_expert_requested_by_at_least_one_annotator_or_disagreement.y,
  row_expert_requested_by_at_least_one_annotator_or_disagreement = row_expert_requested_by_at_least_one_annotator_or_disagreement.x,
  -Value.correct..Yes.No..Ann.1, -Value.corrected.Ann.1, -Corrected.page.Ann.1,
  -Value.correct..Yes.No..Ann.2, -Value.corrected.Ann.2, -Corrected.page.Ann.2,
  -Unit.correct..Yes.No..Ann.1, -Unit.corrected.Ann.1,
  -Unit.correct..Yes.No..Ann.2, -Unit.corrected.Ann.2,
  -Comment.Ann1, -Comment.Ann2,
  -Value.Ann.1, -Value.Ann.2,
  -Unit.Ann.1, -Unit.Ann.2,
  
)
```


### Check expert annotations for discrepancies.
```{r}
annotations %>% filter(is.na(Value..Who.is.right..g1) & !is.na(Value.corrected..fill.in.if.necessary..g1))
```
```{r}
annotations %>% filter(is.na(Value..Who.is.right..g2) & !is.na(Value.corrected..fill.in.if.necessary..g2))
```
```{r}
annotations %>% filter(is.na(Unit..Who.is.right..g1) & !is.na(Unit.corrected..fill.in.if.necessary..g1))
```
Correct to "Unit..Who is right..g1" == "Neither"
```{r}
annotations <- annotations %>% mutate(
  `Unit..Who.is.right..g1` = ifelse(is.na(`Unit..Who.is.right..g1`) & !is.na(`Unit.corrected..fill.in.if.necessary..g1`), "Neither", `Unit..Who.is.right..g1`)
)
```


```{r}
annotations %>% filter(is.na(Unit..Who.is.right..g2) & !is.na(Unit.corrected..fill.in.if.necessary..g2))
```

## Add expert discussion
```{r}
folder_path <- "../../data/raw/expert_discussion/"

files <- list.files(folder_path, full.names = TRUE)

expert_discussion <- data.frame()
for (file in files) {
  
  # Load data
  expert_header <- openxlsx::read.xlsx(file, sheet = 1, rows = 1:6, cols = 1:2, colNames = FALSE)
  expert_body <- openxlsx::read.xlsx(file, sheet = 1, startRow = 7)
  
  # Delete empty rows in body
  expert_body <- expert_body %>% filter(!is.na(LLM.Year))
  
  # Pivot header and combine with body
  expert <- expert_header %>% rename( "Variable" = 1, "Entry" = 2) %>% pivot_wider(names_from = Variable, values_from = Entry) %>% cbind(expert_body)

  # Add to dataframe
  expert_discussion <- rbind(expert_discussion, expert)
  
  # Normalize column names
  colnames(expert_discussion) <- str_replace_all(colnames(expert_discussion), pattern = "\r\n|\n", replacement = " ")
  
}

```

Correct true columns
```{r}
expert_discussion <- expert_discussion %>%
  # replace string "NA" but actual NA value
  mutate(True.unit = ifelse(True.unit == "NA", NA, True.unit),
         True.page = ifelse(True.page == "NA", NA, True.page)) %>%
  
  # transform corrected page to character (previous mistake when reading in data)
  mutate(Corrected.page.Ann.2 = as.character(Corrected.page.Ann.2)) %>% 
  mutate(`Page.corrected.(fill.in.if.necessary).G1` = as.character(`Page.corrected.(fill.in.if.necessary).G1`)) %>%
  
  # undo transformation for template filling from boolean strings to boolean values
  mutate(row_disagreement_value_unit_page_or_unclear = if_else(row_disagreement_value_unit_page_or_unclear ==  "yes", TRUE, FALSE)) %>% 
  
  # select only columns for merging and new columns compared to expert_annotations
  select(`Report Name`, ID, Page.used, LLM.Year, LLM.Scope, LLM.Value, LLM.Unit, True.value, True.unit, True.page, Unresolvable, Comment)
```

Merge to annotations
```{r}
annotations <- left_join(annotations, expert_discussion, by = c(
  "report_name" = "Report Name",
  "ID",
  "page_used" = "Page.used",
  "llm_year" = "LLM.Year",
  "llm_scope" = "LLM.Scope",
  "llm_value" = "LLM.Value",
  "llm_unit" = "LLM.Unit"
))
```

Comment: We don't need to resolve the mismatch for expert discussion because the variables Value.Ann.1/2 and Unit.Ann.1/2 from expert annotations were used when creating templates for expert discussion. Thus, mismatch has already been resolved.

# Save combined dataset
```{r}
write.csv(annotations, "../../data/processed/combined_annotations/annotations.csv", row.names = FALSE)
```

