---
title: "07_expert_discussion_expert_disagreement"
author: "Anna Steinberg"
date: "`r Sys.Date()`"
output: distill::distill_article
---

## Goal of the script: Determine expert disagreement by identifying reports where experts disagree on the true value annotation

### Read packages

```{r}
#Packages
library(tidyverse)
library(readxl)
```

### Define functions to load data, deduce true values, merge and compare the two expert annotations

Deduce correct values from decision of experts
```{r}
deduce_true_values <- function(df) {
  # Rename manual entries with "Ann 1" to "Ann1" in columns `Value: Who is right?` and `Unit: Who is right?` 
  # and accordingly for "Ann 2" (error in template)
  df <- df %>% mutate(`Value: Who is right?` = ifelse(`Value: Who is right?` == "Ann 1", "Ann1", `Value: Who is right?`),
                      `Value: Who is right?` = ifelse(`Value: Who is right?` == "Ann 2", "Ann2", `Value: Who is right?`),
                      `Unit: Who is right?` = ifelse(`Unit: Who is right?` == "Ann 1", "Ann1", `Unit: Who is right?`),
                      `Unit: Who is right?` = ifelse(`Unit: Who is right?` == "Ann 2", "Ann2", `Unit: Who is right?`))
  
  # Deduce true values
  # If Ann1 is right, check whether Ann1 chose yes/no => if yes => choose LLM Value, if no => choose Value corrected Ann 1 (analogously)
  # If Neither chosen, then use Value corrected by experts
  df <- df %>% mutate(true_value = case_when(`Value: Who is right?` == "Ann1" ~ ifelse(`Value correct (Yes/No) Ann 1` == "Yes", `LLM Value`, `Value corrected Ann 1`),
    `Value: Who is right?` == "Ann2" ~ ifelse(`Value correct (Yes/No) Ann 2` == "Yes", `LLM Value`, `Value corrected Ann 2`),
    `Value: Who is right?` == "Neither" ~ `Value corrected (fill in if necessary)`,
  ), 
  # Analogously for unit
  true_unit = case_when(
    `Unit: Who is right?` == "Ann1" ~ ifelse(`Unit correct (Yes/No) Ann 1` == "Yes", `LLM Unit`, `Unit corrected Ann 1`),
    `Unit: Who is right?` == "Ann2" ~ ifelse(`Unit correct (Yes/No) Ann 2` == "Yes", `LLM Unit`, `Unit corrected Ann 2`),
    `Unit: Who is right?` == "Neither" ~ `Unit corrected (fill in if necessary)`,
  ), 
  # If Page set by experts is not NA, then use this page (the experts corrected page)
  # If Page set by experts is NA and neither non-expert is right w.r.t. to value, then use LLM page (aka Page used)
  # Otherwise check whether Ann1 (Ann2) corrected the page and if yes, use corrected page, else LLM page
  true_page = case_when(
    !is.na(`Page corrected (fill in if necessary)`) ~ `Page corrected (fill in if necessary)`,
    is.na(`Page corrected (fill in if necessary)`) & `Value: Who is right?` == "Neither" ~ `Page used`,
    is.na(`Page corrected (fill in if necessary)`) & `Value: Who is right?` == "Ann1" & is.na(`Corrected page Ann 1`) ~ `Page used`,
    is.na(`Page corrected (fill in if necessary)`) & `Value: Who is right?` == "Ann1" & !is.na(`Corrected page Ann 1`) ~ `Corrected page Ann 1`,
    is.na(`Page corrected (fill in if necessary)`) & `Value: Who is right?` == "Ann2" & is.na(`Corrected page Ann 2`) ~ `Page used`,
    is.na(`Page corrected (fill in if necessary)`) & `Value: Who is right?` == "Ann2" & !is.na(`Corrected page Ann 2`) ~ `Corrected page Ann 2`,
  ))
  return(df)
}
```

Load dataframes, transform and merge to one dataframe
```{r}
load_and_transform <- function(path){
  # Set column types
  column_types <- c("text", "text", "numeric", "text", "numeric", "text", "text", "text", "numeric", "text", "text", "numeric", "text", "text", "text", "text", rep("text", 12))
  
  # Load data
  exp_g1_header <- read_excel(path, sheet = 1, n_max = 10)
  exp_g1_body <- read_excel(path, sheet = 1, skip = 10, col_types = column_types)
  
  # Delete empty rows in body
  exp_g1_body <- exp_g1_body %>% filter(!is.na(`LLM Year`))
  
  # Pivot header and combine with body
  exp_g1 <- exp_g1_header %>% rename( "Variable" = 1, "Entry" = 2) %>% pivot_wider(names_from = Variable, values_from = Entry) %>% cbind(exp_g1_body)
  
  # Normalize column names
  colnames(exp_g1) <- str_replace_all(colnames(exp_g1), pattern = "\r\n|\n", replacement = " ")
  
  # Correct time format
  exp_g1 <- exp_g1 %>% 
  rename(started = `Annotation started`, ended = `Annotation ended`) %>%
  mutate(started = as.POSIXct(as.numeric(started) * 86400),
         started = format(started, format = "%H:%M:%S"),
         ended = as.POSIXct(as.numeric(ended) * 86400),
         ended = format(ended, format = "%H:%M:%S"))
  
  # Correct type of Value corrected and Unit corrected
  exp_g1 <- exp_g1 %>% mutate(`Value corrected (fill in if necessary)` = ifelse(
    `Value corrected (fill in if necessary)` == "NA" | 
    `Value corrected (fill in if necessary)` == "N/A", 
    NA, 
    `Value corrected (fill in if necessary)`)) %>%
    mutate(`Value corrected (fill in if necessary)` = as.numeric(`Value corrected (fill in if necessary)`)) %>%
    mutate(`Unit corrected (fill in if necessary)` = ifelse(
      `Unit corrected (fill in if necessary)` == "NA" |
      `Unit corrected (fill in if necessary)` == "N/A", 
      NA, 
      `Unit corrected (fill in if necessary)`)) %>%
    mutate(`Page corrected (fill in if necessary)` = ifelse(
      `Page corrected (fill in if necessary)` == "NA" |
      `Page corrected (fill in if necessary)` == "N/A", 
      NA, 
      `Page corrected (fill in if necessary)`), 
      `Page corrected (fill in if necessary)` = as.character(`Page corrected (fill in if necessary)`))
  
  # Correct Comment Ann2 column of report "cardinal energy ltd_2021_report.pdf"
  if (grepl("cardinal", path)) {
    exp_g1 <- exp_g1 %>% mutate(`Comment Ann2` = ifelse(ID == 1457 & `Comment Ann2` == "LLM made calculation from 188 times 10^3", "LLM made calculation from 188 times 10^4", `Comment Ann2`), 
                                `Comment Ann2` = ifelse(ID == 1458 & `Comment Ann2` == "LLM made calculation from 188 times 10^3", "LLM made calculation from 188 times 10^5", `Comment Ann2`))    
  }


  exp_g1 <- deduce_true_values(exp_g1)
  return(exp_g1)
}
```

Merge dataframes and compare values to find disagreement
```{r}
merge_and_compare <- function(exp_g1, exp_g2) {
  idx_for_join <- c(1:4, 10:22, 26:29, 33:34)
  names_for_join <- names(exp_g1)[idx_for_join]

  exp <- left_join(exp_g1, exp_g2, by = names_for_join, suffix = c(".g1", ".g2")) %>% 
    mutate(agreement_value = case_when(
      is.na(true_value.g1) & is.na(true_value.g2) ~ TRUE,
      !is.na(true_value.g1) & is.na(true_value.g2) | is.na(true_value.g1) & !is.na(true_value.g2) ~ FALSE,
      true_value.g1 == true_value.g2 ~ TRUE,
      .default = FALSE),
    agreement_unit = case_when(
      is.na(true_unit.g1) & is.na(true_unit.g2) ~ TRUE,
      !is.na(true_unit.g1) & is.na(true_unit.g2) | is.na(true_unit.g1) & !is.na(true_unit.g2) ~ FALSE,
      true_unit.g1 == true_unit.g2 ~ TRUE,
      .default = FALSE),
    agreement_page = case_when(
      is.na(true_page.g1) & is.na(true_page.g2) ~ TRUE,
      !is.na(true_page.g1) & is.na(true_page.g2) | is.na(true_page.g1) & !is.na(true_page.g2) ~ FALSE,
      true_page.g1 == true_page.g2 ~ TRUE, 
      .default = FALSE),
    agreement_value_unit = agreement_value & agreement_unit,
    agreement_value_unit_page = agreement_value & agreement_unit & agreement_page,
    at_least_one_group_flagged_unclear = case_when(
      `Unclear record (Yes/No).g1` == "Yes" | `Unclear record (Yes/No).g2` == "Yes" ~ TRUE,
      .default = FALSE,
    ))
  return(exp)
}
```

Function to find corresponding report according to template naming
```{r}
read_and_compare <- function(folder_path) {
  exp_annotation <- data.frame()

  files_list <- list.files(folder_path, full.names = TRUE)
  
  # Find pairs of reports where the same report has been annotated by two expert groups
  process_order <- data.frame(path = files_list) %>% 
    # Process filenames to remove numeric prefix and .xlsx suffix
    mutate(base_path = basename(path),
      report_name = gsub("^\\d+_", "", base_path), # Remove the numeric prefix and underscore
      report_name = gsub("\\.xlsx$", ".pdf", report_name)) # Remove the .xlsx suffix
  
  for (report in unique(process_order$report_name)) {
    paths <- process_order %>% filter(report_name == report) %>% select(path) %>% pull()
    exp_g1 <- load_and_transform(paths[1])
    exp_g2 <- load_and_transform(paths[2])
    
    exp <- merge_and_compare(exp_g1, exp_g2)
    exp_annotation <- rbind(exp, exp_annotation)
  }
  return(exp_annotation)
}
```

### Loop through expert annotation folder
```{r}
folder_path <- "../../data/raw/expert_annotation"
exp <- read_and_compare(folder_path)
```

### Expert Disagreement

Checks for correct computation of agreement variables
```{r}
exp %>% filter(is.na(agreement_value) | is.na(agreement_unit) | is.na(agreement_page) | is.na(agreement_value_unit) | is.na(agreement_value_unit_page) | is.na(at_least_one_group_flagged_unclear))
```



Check for number of reports
```{r}
exp %>% distinct(`Report Name`)
```
The number of reports has to correspond to 56.

Reports for discussion
- disagreement on value and unit 
OR
- at least one group flagged unclear record

```{r}
exp %>% group_by(`Report Name`) %>% filter(any(agreement_value_unit == FALSE) | any(at_least_one_group_flagged_unclear == TRUE)) %>% distinct(`Report Name`) %>% arrange(`Report Name`)
```

Reports for which experts agree on value and unit, but disagree on page
```{r}
exp %>% group_by(`Report Name`) %>% filter(any(agreement_value_unit == TRUE) & any(agreement_page == FALSE)) %>% distinct(`Report Name`)
```

*Definition of expert disagreement*
- disagreement on value or unit or page
OR
- at least one group flagged unclear record
```{r}
exp %>% group_by(`Report Name`) %>% filter(any(agreement_value_unit_page == FALSE) | any(at_least_one_group_flagged_unclear == TRUE)) %>% distinct(`Report Name`)
```

### Prepare dataframe for template filling
- Create columns "Value Ann 1" and "Value Ann 2" with respective values instead of indicator (same for unit)
- Create row highlighting based on expert group disagreement or disagreement on unclear record
- Rearrange dataframe

```{r}
# columns with entries instead of indicators
exp <- exp %>% 
  mutate(`Value Ann 1` = ifelse(`Value correct (Yes/No) Ann 1` == "Yes", `LLM Value`, `Value corrected Ann 1`),
         `Value Ann 2` = ifelse(`Value correct (Yes/No) Ann 2` == "Yes", `LLM Value`, `Value corrected Ann 2`),
         `Unit Ann 1` = ifelse(`Unit correct (Yes/No) Ann 1` == "Yes", `LLM Unit`, `Unit corrected Ann 1`),
         `Unit Ann 2` = ifelse(`Unit correct (Yes/No) Ann 2` == "Yes", `LLM Unit`, `Unit corrected Ann 2`),
  )

# variable for row highlighting
exp <- exp %>%
  mutate(row_disagreement_value_unit_page_or_unclear = agreement_value_unit_page == FALSE | at_least_one_group_flagged_unclear == TRUE)
```

Save dataset for later use
```{r}
write.csv(exp, "../../data/processed/expert_discussion/expert_disagreement.csv", row.names = FALSE)
```

Rearrange dataframe
```{r}
exp_discussion <- exp %>%
  select(`Report Name`, `Document comment Annotator 1`, `Document comment Annotator 2`, `Expert document comment.g1`, `Expert document comment.g2`, `Document-level expert adjudication requested by at least 1 annotator`, 
         ID, `Page used`, `LLM Year`, `LLM Scope`, `LLM Value`, `LLM Unit`, 
         `Value Ann 1`, `Value Ann 2`, 
         `Value: Who is right?.g1`, `Value corrected (fill in if necessary).g1`, `Value Reasoning (select if necessary, if multiple apply choose first).g1`, 
         `Value: Who is right?.g2`, `Value corrected (fill in if necessary).g2`, `Value Reasoning (select if necessary, if multiple apply choose first).g2`, 
         `Unit Ann 1`, `Unit Ann 2`, 
         `Unit: Who is right?.g1` , `Unit corrected (fill in if necessary).g1`, `Unit reasoning  (select if necessary, if multiple apply choose first).g1`,
         `Unit: Who is right?.g2`, `Unit corrected (fill in if necessary).g2`, `Unit reasoning  (select if necessary, if multiple apply choose first).g2`,
         `Corrected page Ann 1`, `Corrected page Ann 2`, `Page corrected (fill in if necessary).g1`, `Page corrected (fill in if necessary).g2`, 
         `Comment Ann1`, `Comment Ann2`, `Expert comment.g1`, `Expert comment.g2`, 
         `Unclear record (Yes/No).g1`, `Unclear record (Yes/No).g2`,
         row_disagreement_value_unit_page_or_unclear, 
         starts_with("agreement"))
```

Save dataframe
```{r}
write.csv(exp_discussion, "../../data/processed/expert_discussion/data_for_expert_discussion_template.csv", row.names = FALSE)
```