---
title: "08_expert_discussion_template_filling"
author: "Laia Domenech Burin"
date: "`r Sys.Date()`"
output: distill::distill_article
---

## Goal of the script: Set up expert discussion template and transfer records from reports that were analyzed by experts to template

### Load packages

```{r}
library(tidyverse)
library(readxl)
library(openxlsx)
```

# Create functions that fill the header and organize the header columns

```{r}

fill_template_header <- function(data = expert_disagreement){
  
  disagreement_header <- data %>%
  select(1:6) %>%
  group_by(`Report Name`) %>%
  reframe(across(everything(), ~unique(.)))

  return(disagreement_header)
}

rename_and_organize_header_columns <- function(header = disagreement_header){
  
    filled_header <- header %>%
      rename_with(.cols = contains(".g1"), .fn = ~ str_replace(., "\\.g1$", " G1")) %>%
      rename_with(.cols = contains(".g2"), .fn = ~ str_replace(., "\\.g2$", " G2")) %>%
      pivot_longer(cols = c(1:6),
                 names_to = ' ',
                 values_to = '  ') %>%
      
    
    return(filled_header)

}
```

# Create functions that fill the table and organize the table columns

```{r}
fill_template_table <- function(template_table = template_table,
                                data = expert_disagreement) {
  
  template_table <- template_table %>% select('LLM Year', 'LLM Scope',
                          'True value', 'True unit',
                          'Unresolvable',
                          'True page', 'Comment')
  
  table_join <- template_table %>% full_join(data,
                                           by = c('LLM Year', 'LLM Scope'))
  
  table_join <- table_join %>% filter(!is.na(ID))
  

  return(table_join)

}

rename_and_organize_table_columns <- function(data = filled_table){
    
      filled_table <- data %>% select(-starts_with("agreement")) %>% 
        rename_with(.cols = ends_with(".g1"), .fn = ~ str_replace(., "\\.g1$", " G1")) %>%
        rename_with(.cols = ends_with(".g2"), .fn = ~ str_replace(., "\\.g2$", " G2")) %>%
        select(ID, `Page used`, starts_with('LLM'), 
               starts_with('Value'), `True value`,
               starts_with('Unit'), `True unit`,
               starts_with('Corrected'), starts_with('Page corrected'), `True page`,
               starts_with('Comment '), starts_with('Expert comment'),
               starts_with('Unclear'),
               Unresolvable, 
               Comment,
               row_disagreement_value_unit_page_or_unclear)
    
    return(filled_table)

}

```

# Write output

```{r}

write_template_per_doc <- function(template_path, filled_header,
                                    filled_table, folder_path){
  
  wb <- loadWorkbook(template_path)
  dir.create(folder_path, showWarnings = FALSE)
  
  writeData(wb, sheet = "Tabelle1", 
                      x = filled_header, 
                      startCol = 1, startRow = 1, 
                      colNames = FALSE, rowNames = FALSE)
            
  writeData(wb, sheet = "Tabelle1",
            x = filled_table,
            startCol = 1, startRow = 8,
            colNames = TRUE, rowNames = FALSE)
        
  
  doc_export_data <- filled_header %>% slice(1) %>% pull(2)
  
  saveWorkbook(wb, file = paste0(folder_path, "/", str_replace(doc_export_data, "\\.pdf$", ""),".xlsx"), overwrite = TRUE)
}

```

# Run filler functions on templates and export all of them

```{r}
fill_and_export_templates_for_doc <- function(data = expert_disagreement, report, template_path, folder_path){
  
  filtered_expert_disagreement <- data %>% filter(`Report Name` == report)
  
  filled_template_header <- fill_template_header(filtered_expert_disagreement)
  
  filled_template_header <- rename_and_organize_header_columns(filled_template_header)
  
  template_table <- read_excel(template_path, skip = 7) 
  filled_template_table <- fill_template_table(template_table = template_table, data = filtered_expert_disagreement)
  
  filled_template_table <- rename_and_organize_table_columns(filled_template_table)
  
  write_template_per_doc(template_path = template_path, 
                         filled_header = filled_template_header,
                         filled_table = filled_template_table,
                         folder_path = folder_path)
}
```

# Run on all the reports

```{r}
# Read in data
expert_disagreement <- read.csv("../../data/processed/expert_discussion/data_for_expert_discussion_template.csv", check.names = FALSE)

# Transformation for highlighting in Excel sheet
expert_disagreement <- expert_disagreement %>% mutate(row_disagreement_value_unit_page_or_unclear = if_else(row_disagreement_value_unit_page_or_unclear ==  TRUE, 'yes', 'no'))

# Filter for reports which contain disagreement
expert_disagreement <- expert_disagreement %>% group_by(`Report Name`) %>% filter(any(row_disagreement_value_unit_page_or_unclear == 'yes')) %>% ungroup()

# Get unique report names
unique_reports <- unique(expert_disagreement$`Report Name`)

# Set path to template
template_path <- '../../data/templates/expert_discussion_template.xlsx'

# For illustrative purposes: set folder_path to save filled templates to
folder_path <- '../../data/templates/filled_expert_discussion_templates'

# Apply the function on each unique report using walk()
walk(unique_reports, ~ fill_and_export_templates_for_doc(data = expert_disagreement, report = .x, template_path = template_path, folder_path = folder_path))
```
