---
title: "04_expert_annotations_expert_demand"
author: "Jacob Beck"
date: "`r Sys.Date()`"
output: distill::distill_article
---

## Goal of the script: Determine our expert demand. It is needed where a) asked for or b) meaningful disagreement.


### Read data and packages

```{r}
#Packages
library(tidyverse)
```

```{r}
# Read data
df <- read.csv("../../data/processed/non_expert_annotations/non_expert_annotations_cleaned.csv")
```

To compute expert demand we need to pivot the data to have one row per report and then check where non-experts requested expert adjudication.

```{r}
source("../pivot.R")

# variables which concern expert adjudication
pivot_vars <- c("document_expert_needed", "record_expert_needed")
df_pivot <- pivot_w_split(df, pivot_vars)
```


### Part a) Where did annotators ask for expert demand?

```{r}
exp_requested_document <- df_pivot %>%
  filter(document_expert_needed_1 == "Yes" | document_expert_needed_2 == "Yes") %>%
  select(report_name) %>%
  distinct()

# Create a variable that marks whether the expert is needed (can be added with the computed expert demand) 
# Needed if requested on doc level or if record_expert_needed == "Yes"

df2 <- df_pivot %>%
  mutate(expert_needed = ifelse(
    test = (report_name %in% exp_requested_document$report_name | # expert needed if the report name is among the requested ones
              rowSums(select(., starts_with("record_expert_needed")) == "Yes", na.rm = TRUE) > 0), # expert needed if at least one of the record needed cols contains "Yes" 
    TRUE, FALSE))

table(df2$expert_needed)
```


### Part b) Where do we have meaningful disagreement (in value or unit correct columns)?

To compute disagreement, we need to pivot our cleaned data using value_correct and unit_correct as pivot variables and then compute agreement between the two non-experts for these variables. 
```{r}
# Pivot data
pivot_vars_2 <- c("value_correct", "unit_correct")
df3 <- pivot_w_split(df, pivot_vars_2)

# Compute agreement for each variable individually
df3 <- agreement_func(df3, "value_correct")
df3 <- agreement_func(df3, "unit_correct")

# Compute combined agreement
df3$agreement_value_and_unit <- df3$agreement_value_correct & df3$agreement_unit_correct

# Join new variables to data containing expert_needed variable
df4 <- left_join(df2, df3, by = c("report_name", "ID", "page_used", "llm_year", "llm_scope", "llm_value", "llm_unit", "annotator_ID_1", "annotator_ID_2"))

# Compute expert demand by including disagreement
df4 <- df4 %>%
  mutate(
    expert_needed = ifelse(
      agreement_value_and_unit == FALSE, # if either unit or value disagree
    TRUE, expert_needed)) # then expert is needed. if not just keep the expert needed value from above (to not overwrite existing TRUEs)

table(df4$expert_needed)
```

```{r}
df4  %>% filter(expert_needed == T) %>% 
  distinct(report_name)
```

Save data including expert_needed variable
```{r}
write.csv(df4, "../../data/processed/expert_annotations/expert_demand.csv", row.names = FALSE)
```

