---
title: "descriptives_for_paper_n_codebooks.Rmd"
author: "Anna Steinberg"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Goal of the Script: Produce descriptive statistics for the paper and the codebooks

```{r warning=FALSE}
library(tidyverse)
library(pdftools)
library(xtable)
```

# Load datasets
```{r}
# Gold standard
gs <- read.csv("../../data/processed/combined_annotations/gold_standard.csv")

# Annotation dataset
ads <- read.csv("../../data/processed/combined_annotations/annotation_dataset.csv")
```

# Gold standard - Descriptives

## Distribution of values by

### Report
```{r}
count_by_report <- gs %>%
  group_by(company_name, report_year) %>%
  summarize(count = sum(!is.na(value)))

ggplot(count_by_report, aes(x  = count)) +
  geom_histogram(binwidth = 1, fill = "darkgreen", color = "black") +
  stat_bin(binwidth = 0.5, geom = "text", aes(label = after_stat(count)), vjust = -0.5) +
  labs(title = "Distribution of values by Report",
       x = "Number of values",
       y = "Number of reports") +
 
  
   theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))  # Rotate x-axis labels if needed

```
Distribution of non-NA
```{r}
count_by_report_nonNA <- count_by_report %>% filter(count > 0)

summary(count_by_report_nonNA$count)
```
### Scope

```{r}
count_by_scope <- gs %>%
  filter(company_name %in% count_by_report_nonNA$company_name, 
         report_year %in% count_by_report_nonNA$report_year) %>%
  group_by(company_name, report_year, scope) %>%
  summarize(count = sum(!is.na(value)), .groups = "drop") %>%
  group_by(scope) %>%
  summarize(avg_scope_count = mean(count, na.rm = TRUE))

xtable(count_by_scope)
```

### Year

```{r}
count_by_year <- gs %>%
  group_by(year) %>%
  summarize(non_missing_count_year = sum(!is.na(value)))

# Calculate the total counts to use for percentage calculation
total_counts <- sum(count_by_year$non_missing_count_year)

# Add a new column for the percentage
count_by_year <- count_by_year %>%
  mutate(percent = non_missing_count_year / total_counts * 100)

# Plotting the data with percentages
ggplot(count_by_year %>% filter(non_missing_count_year > 0), aes(x = as.factor(year), y = percent)) +
  geom_bar(stat = "identity", fill = "steelblue") +
  geom_text(aes(label = sprintf("%.1f%%", percent)), vjust = -0.5, color = "black") +
  labs(title = "Percentage of Values Extracted by Year",
       x = "Year",
       y = "Percentage (%)") +
  theme_minimal()
```
```{r}
count_by_year %>% filter(year >= 2017 & year <= 2021) %>% summarise(sum(percent))
```
### Display type
```{r}
count_by_display_type <- gs %>%
  group_by(display_type) %>%
  summarize(non_missing_count_display_type = sum(!is.na(value)))

# Calculate the total counts to use for percentage calculation
total_counts <- sum(count_by_display_type$non_missing_count_display_type)

# Add a new column for the percentage
count_by_display_type <- count_by_display_type %>%
  mutate(percent = non_missing_count_display_type / total_counts * 100)

# Plotting the data with percentages
ggplot(count_by_display_type %>% filter(non_missing_count_display_type > 0), aes(x = as.factor(display_type), y = percent)) +
  geom_bar(stat = "identity", fill = "steelblue") +
  geom_text(aes(label = sprintf("%.1f%%", percent)), vjust = -0.5, color = "black") +
  labs(title = "Percentage of Values by display type",
       x = "Year",
       y = "Percentage (%)") +
  theme_minimal()
```

## Report types
```{r}
count_by_report_type <- gs %>%
  group_by(company_name, report_year, report_type) %>% 
  summarize(count_report_type = n_distinct(report_type)) %>%
  group_by(report_type) %>%
  summarize(count_report_type = sum(count_report_type, na.rm = TRUE))
              

coarse_report_types <- count_by_report_type %>%
  mutate(category = ifelse(grepl("annual", tolower(report_type)), "Annual", "Other")) %>%
  group_by(category) %>%
  summarize(coarse_report_types = sum(count_report_type, na.rm = TRUE))

granular_report_types <- count_by_report_type %>%
  filter(!grepl("annual", tolower(report_type))) %>%
  arrange(desc(count_report_type))
```

## Unique values and range for codebook

```{r}
#company name
gs %>% distinct(company_name)

#report year range
summary(gs$report_year)

# report year
gs %>% distinct(report_type)

# url
gs %>% distinct(url)

# year
summary(gs$year)

# scope
unique(gs$scope)

# page
unique(gs$page)

# value
summary(gs$value)

# unit
unique(gs$unit)

# normalized unit
unique(gs$unit_normalized)

# metric name
unique(gs$metric_name)

# display type
unique(gs$display_type)
```
# Annotation dataset - Descriptives

How often do experts agree with one annotator and how often do they choose a different value

Compare gold standard value with non-experts' values for rows passed on to expert adjudication and see how often experts agree with non-experts
```{r}
# Join gold standard
agreement <- ads %>% left_join(gs, by = c("company_name", "report_year", "merge_id"))

# Compare gold standard value with non-experts' values for rows passed on to expert adjudication
agreement <- agreement %>% filter(non_exp_filter_rec == "Yes" | non_exp_filter_doc == "Yes") %>%
  mutate(
    agreement_exp_w_min_1_non_exp = case_when(
      is.na(value) & !is.na(non_exp_1_value) ~ FALSE,
      is.na(value) & is.na(non_exp_1_value) ~ TRUE,
      is.na(value) & !is.na(non_exp_2_value) ~ FALSE,
      is.na(value) & is.na(non_exp_2_value) ~ TRUE,
      value == non_exp_1_value ~ TRUE,
      value == non_exp_2_value ~ TRUE,
      value != non_exp_1_value ~ FALSE,
      value != non_exp_2_value ~ FALSE,
    )
  )

# Check correct computation
agreement %>% filter(is.na(agreement_exp_w_min_1_non_exp))
```

```{r}
agreement %>% group_by(agreement_exp_w_min_1_non_exp) %>% summarize(n = n(), .groups = "drop") %>% reframe(percentage = n / sum(n) * 100)
```
<<<<<<< HEAD
=======

## Unique values and ranges for codebook

```{r}
# llm page
unique(ads$llm_page)

# llm year
summary(ads$llm_year)

# llm value
summary(ads$llm_value)

# llm unit
unique(ads$llm_unit)

# non exp corrected value
summary(ads$non_exp_1_corrected_value)
summary(ads$non_exp_2_corrected_value)

# non exp corrected unit
unique(ads$non_exp_1_corrected_unit)
unique(ads$non_exp_2_corrected_unit)

# non exp corrected page
unique(ads$non_exp_1_corrected_page)
unique(ads$non_exp_2_corrected_page)

# non exp metric name
unique(ads$non_exp_1_metric_name)
unique(ads$non_exp_2_metric_name)

# non exp display type
unique(ads$non_exp_1_display_type)
unique(ads$non_exp_2_display_type)

# non exp value
summary(ads$non_exp_1_value)
summary(ads$non_exp_2_value)

# non exp unit
unique(ads$non_exp_1_unit)
unique(ads$non_exp_2_unit)

# non exp page
unique(ads$non_exp_1_page)
unique(ads$non_exp_2_page)

# exp group corrected value
summary(ads$exp_group_1_corrected_value)
summary(ads$exp_group_2_corrected_value)

# exp group corrected unit
unique(ads$exp_group_1_corrected_unit)
unique(ads$exp_group_2_corrected_unit)

# exp group corrected page
unique(ads$exp_group_1_corrected_page)
unique(ads$exp_group_2_corrected_page)

# exp group value
summary(ads$exp_group_1_value)
summary(ads$exp_group_2_value)

# exp group unit
unique(ads$exp_group_1_unit)
unique(ads$exp_group_2_unit)

# exp group page
unique(ads$exp_group_1_page)
unique(ads$exp_group_2_page)

# exp disc value
summary(ads$exp_disc_value)

# exp disc unit
unique(ads$exp_disc_unit)

# exp disc page
unique(ads$exp_disc_page)
```

>>>>>>> 930d363 (feat: adapt descriptives to new structure and add codebooks metrics)
