---
title: "gs8_gold_standard"
author: "Anna Steinberg"
date: "`r Sys.Date()`"
output: distill::distill_article
---

# Goal of the script: Create gold standard dataset

Columns of gold standard dataset:
- report name
- report type (annual vs. sustainability)
- url
- year
- scope
- page
- value
- unit
- unit (normalized)
- metric name (optionally separated by "/")
- display type (Table, Text, Graphic) (optionally separated by "/")
- raw extracted text from page (column: PageTextsToLLM in cleaned_data)

# Load libraries
```{r}
library(tidyverse)
library(readxl)
```

# Load annotations with gold standard
```{r}
annotations <- read.csv("../../data/processed/gold_standard/annotations_incl_gold_standard.csv")
```

Rename variables
```{r}
gold_standard <- annotations %>%
  select(
    report_name,
    year = llm_year,
    scope = llm_scope,
    value = true_value,
    unit = true_unit,
    page = true_page,
    metric_name_1, 
    metric_name_2, 
    reporting_type_1,
    reporting_type_2,
    merge_id = merge_ID
  )
```


## Adding additional columns
Columns of gold standard dataset:
- report name
- report type (annual vs. sustainability)
- url
- year
- scope
- page
- value
- unit
- unit (normalized)
- metric name (optionally separated by "/")
- display type (Table, Text, Graphic) (optionally separated by "/")
- raw extracted text from page (column: PageTextsToLLM in cleaned_data)

### Metric name and display type

```{r}
gs_metricname_displaytype <- gold_standard %>% 
  mutate(metric_name = case_when(
    !is.na(metric_name_1) & is.na(metric_name_2) ~ metric_name_1,
    is.na(metric_name_1) & !is.na(metric_name_2) ~ metric_name_2,
    !is.na(metric_name_1) & !is.na(metric_name_2) & metric_name_1 == metric_name_2 ~ metric_name_1,
    !is.na(metric_name_1) & !is.na(metric_name_2) & metric_name_1 != metric_name_2 ~ paste0(metric_name_1, "/", metric_name_2),
    is.na(metric_name_1) & is.na(metric_name_2) ~ NA),
  display_type = case_when(
    !is.na(reporting_type_1) & is.na(reporting_type_2) ~ reporting_type_1,
    is.na(reporting_type_1) & !is.na(reporting_type_2) ~ reporting_type_2,
    !is.na(reporting_type_1) & !is.na(reporting_type_2) & reporting_type_1 == reporting_type_2 ~ reporting_type_1,
    !is.na(reporting_type_1) & !is.na(reporting_type_2) & reporting_type_1 != reporting_type_2 ~ paste0(reporting_type_1, "/", reporting_type_2),
    is.na(reporting_type_1) & is.na(reporting_type_2) ~ NA)
  )

gs_metricname_displaytype <- gs_metricname_displaytype %>% select(report_name, year, scope, page, value, unit, metric_name, display_type, merge_id) 
```
If value is NA, metric_name and display_type should be NA as well
```{r}
gs_metricname_displaytype <- gs_metricname_displaytype %>%
  mutate(
    metric_name = ifelse(is.na(value), NA, metric_name),
    display_type = ifelse(is.na(value), NA, display_type)
  )
```
### Duplicates
```{r}
inspect <- gs_metricname_displaytype %>% distinct() %>% group_by(report_name, year, scope, value, page) %>% summarise(n = n()) %>% filter(n > 1)

inspect <- left_join(inspect, gs_metricname_displaytype, by = c("report_name", "year", "scope", "value", "page"))
```

Manual inspection:
- "acuity" => combine rows into one by combining display_type (annotation mistake)
- "aixtron" => expert advocated for unit "tonnes of CO2 equivalents"
- "allfunds" => expert advocated for unit "t CO2eq"
- "independence 2017" => correct display type = Text
- "jetblue" => correct metric name = "Direct (Scope 1)"
- "sumitomo" => correct unit "t-CO2e" and metric name "Scope2"

Manual correction:
```{r}
# Removing rows from gs_metricname_displaytype that are present in inspect
gs_subset <- anti_join(gs_metricname_displaytype, inspect, by = c("report_name", "year", "scope", "value", "page"))

# Correcting rows in inspect
inspect_corrected <- inspect %>%
  mutate(
    display_type = ifelse(grepl("acuity", report_name), "Table/Text", display_type),
    unit = ifelse(grepl("aixtron", report_name), "tonnes of CO2 equivalents", unit),
    unit = ifelse(grepl("allfunds", report_name), "t CO2eq", unit),
    metric_name = ifelse(grepl("allfunds", report_name), "Scope 2", metric_name),
    display_type = ifelse(grepl("independence", report_name), "Text", display_type),
    metric_name = ifelse(grepl("jetblue", report_name), "Direct (Scope 1)", metric_name),
    unit = ifelse(grepl("sumitomo", report_name), "t-CO2e", unit),
    metric_name = ifelse(grepl("sumitomo", report_name), "Scope2", metric_name), 
    display_type = ifelse(grepl("sumitomo", report_name), "Table", display_type)
  )

# Remove duplicates
inspect_unique <- inspect_corrected %>% distinct()

# Add back to gs_metricname_displaytype
gs_unique <- bind_rows(gs_subset, inspect_unique)
```


### Report type and url
To add report type and url, we need to load the excel sheet containing this info
```{r}
report_info <- read_excel("../../data/processed/reports_w_URLs_report-type.xlsx")
```

Join by report name
```{r}
report_info_join <- report_info %>%
  mutate(report_name = paste0(file_name, ".pdf")) %>%
  select(report_name, url, report_type_specific)

gs_reporttype_url <- left_join(gs_unique, report_info_join, by = "report_name") %>%
  rename(report_type = report_type_specific)
```

### Unit (normalized)

Load normalization dictionary
```{r}
normalization_dict <- read.csv("../../data/processed/unit_normalization.csv")
```

Merge normalized units to dataset
```{r}
gs_normalized <- gs_reporttype_url %>%
  mutate(unit_normalized_match = ifelse(
    !is.na(unit), normalization_dict$normalized_unit[match(unit, normalization_dict$unit)], unit),
    unit_normalized = ifelse(!is.na(unit_normalized_match), unit_normalized_match, unit)) %>%
  select(-unit_normalized_match)
```

### Page text
```{r}
cleaned_data <- read.csv("../../data/processed/cleaned_data.csv")
```


```{r}
page_text_join <- cleaned_data %>% select(report_name, page_used, PageTextsToLLM) %>% distinct()

page_text_join %>% group_by(report_name, page_used) %>% summarise(n = n()) %>% filter(n > 1)
```
For the Allianz report the page 92 once has text extracted and once not. Just remove the row with NA text.

```{r}
page_text_join <- page_text_join %>% filter(!(grepl("Allianz", report_name) & page_used == 92 & is.na(PageTextsToLLM)))
```

Join page text to dataset
The column page text should only contain the page text extracted if page_used coincides with page

```{r}
gs_pagetext <- left_join(gs_normalized, page_text_join, by = c("report_name" = "report_name", "page" = "page_used")) %>%
  select(report_name, report_type, url, year, scope, page, value, unit, unit_normalized, metric_name, display_type, extracted_text_from_page = PageTextsToLLM, merge_id)
```

### Company name and report year
```{r}
gs_companyname_reportyear <- gs_pagetext %>% separate(
  report_name, c("company_name", "report_year", "suffix"), sep = "_", remove = FALSE) %>%
  select(-report_name, -suffix)
```

Correct discrepancy between report_name and company_name for "vital energy" to "uniper"
```{r}
gs_companyname_reportyear <- gs_companyname_reportyear %>%
  mutate(company_name = ifelse(grepl("vital energy", company_name), "uniper", company_name))
```

### Save gold standard

Remove duplicates and arrange by report_name, year, scope, page
```{r}
gold_standard_final <- gs_companyname_reportyear %>% distinct() %>% arrange(company_name, report_year, scope, year, page)
```

```{r}
write_csv(gold_standard_final, "../../data/processed/gold_standard/gold_standard.csv")
```

