---
title: "gs9_annotation_dataset"
author: "Anna Steinberg"
date: "`r Sys.Date()`"
output: distill::distill_article
---

# Goal of the script: Create annotation dataset for publication

# Load libraries
```{r}
library(tidyverse)
library(readxl)
```

```{r}
source("../pivot.R")
```

# Load dataset
```{r}
annotations <- read.csv("../../data/processed/gold_standard/annotations_incl_gold_standard.csv")
cleaned_data <- read.csv("../../data/processed/cleaned_data.csv")
```

# Add the following columns:
- value_reasoning
- unit_reasoning

```{r}
pivot_vars <- c("value_reasoning", "unit_reasoning")
missing_columns <- pivot_w_split(cleaned_data, pivot_vars)
annotations <- left_join(annotations, missing_columns, by = c("report_name", "ID", "page_used", "llm_year", "llm_scope", "llm_value", "llm_unit", "annotator_ID_1", "annotator_ID_2"))
```

- pages_searched
```{r}
pages_searched <- cleaned_data %>% select(report_name, pages_searched) %>% distinct()
annotations <- left_join(annotations, pages_searched, by = c("report_name"))
```

# Change ID column
```{r}
annotations <- annotations %>% 
  mutate(non_exp_manually_added_record = ifelse(grepl("x", ID), TRUE, FALSE)) # manually added rows start with "x"
```


# Rename columns
```{r}
annotations <- annotations %>% 
  rename(
    llm_page = page_used,
    non_exp_1_id = annotator_ID_1,
    non_exp_2_id = annotator_ID_2,
    non_exp_1_is_value_correct = value_correct_1,
    non_exp_2_is_value_correct = value_correct_2,
    non_exp_1_corrected_value = corrected_value_1,
    non_exp_2_corrected_value = corrected_value_2,
    non_exp_1_value_reasoning = value_reasoning_1,
    non_exp_2_value_reasoning = value_reasoning_2,
    non_exp_1_value = Value.Ann.1,
    non_exp_2_value = Value.Ann.2,
    non_exp_1_is_unit_correct = unit_correct_1,
    non_exp_2_is_unit_correct = unit_correct_2,
    non_exp_1_corrected_unit = corrected_unit_1,
    non_exp_2_corrected_unit = corrected_unit_2,
    non_exp_1_unit_reasoning = unit_reasoning_1,
    non_exp_2_unit_reasoning = unit_reasoning_2,
    non_exp_1_unit = Unit.Ann.1,
    non_exp_2_unit = Unit.Ann.2,
    non_exp_1_is_page_correct = page_correct_1,
    non_exp_2_is_page_correct = page_correct_2,
    non_exp_1_corrected_page = corrected_page_1,
    non_exp_2_corrected_page = corrected_page_2,
    non_exp_1_page = Page.Ann.1,
    non_exp_2_page = Page.Ann.2,
    non_exp_1_expert_requested_for_rec = record_expert_needed_1,
    non_exp_2_expert_requested_for_rec = record_expert_needed_2,
    non_exp_1_expert_requested_for_doc = document_expert_needed_1,
    non_exp_2_expert_requested_for_doc = document_expert_needed_2,
    non_exp_1_metric_name = metric_name_1,
    non_exp_2_metric_name = metric_name_2,
    non_exp_1_display_type = reporting_type_1,
    non_exp_2_display_type = reporting_type_2,
    non_exp_filter_doc = document_expert_requested_by_at_least_one_annotator,
    non_exp_filter_rec = row_expert_requested_by_at_least_one_annotator_or_disagreement,
    exp_group_1_exp_1_id = Expert.ID.1.g1,
    exp_group_1_exp_2_id = Expert.ID.2.g1,
    exp_group_2_exp_1_id = Expert.ID.1.g2,
    exp_group_2_exp_2_id = Expert.ID.2.g2,
    exp_group_1_value_who_is_right = Value..Who.is.right..g1,
    exp_group_1_corrected_value = Value.corrected..fill.in.if.necessary..g1,
    exp_group_1_value_reasoning = Value.Reasoning..select.if.necessary..if.multiple.apply.choose.first..g1,
    exp_group_1_value = Value.G1,
    exp_group_2_value_who_is_right = Value..Who.is.right..g2,
    exp_group_2_corrected_value = Value.corrected..fill.in.if.necessary..g2,
    exp_group_2_value_reasoning = Value.Reasoning..select.if.necessary..if.multiple.apply.choose.first..g2,
    exp_group_2_value = Value.G2,
    exp_group_1_unit_who_is_right = Unit..Who.is.right..g1,
    exp_group_1_corrected_unit = Unit.corrected..fill.in.if.necessary..g1,
    exp_group_1_unit_reasoning = Unit.reasoning...select.if.necessary..if.multiple.apply.choose.first..g1,
    exp_group_1_unit = Unit.G1,
    exp_group_2_unit_who_is_right = Unit..Who.is.right..g2,
    exp_group_2_corrected_unit = Unit.corrected..fill.in.if.necessary..g2,
    exp_group_2_unit_reasoning = Unit.reasoning...select.if.necessary..if.multiple.apply.choose.first..g2,
    exp_group_2_unit = Unit.G2,
    exp_group_1_corrected_page = Page.corrected..fill.in.if.necessary..g1,
    exp_group_1_page = Page.G1,
    exp_group_2_corrected_page = Page.corrected..fill.in.if.necessary..g2,
    exp_group_2_page = Page.G2,
    exp_group_filter_rec = row_disagreement_value_unit_page_or_unclear,
    exp_disc_value = True.value,
    exp_disc_unit = True.unit,
    exp_disc_page = True.page,
    merge_id = merge_ID
  )
```

# Save dataset with comments only
```{r}
comments <- annotations %>%
  select(report_name, llm_year, llm_scope, 
         non_exp_1_comment_rec = comment_1, non_exp_2_comment_rec = comment_2, 
         non_exp_1_comment_doc = document_comment_1, non_exp_2_comment_doc = document_comment_2,
         exp_group_1_comment_rec = Expert.comment.g1, exp_group_2_comment_rec = Expert.comment.g2,
         exp_group_1_comment_doc = Expert.document.comment.g1, exp_group_2_comment_doc = Expert.document.comment.g2)

write.csv(comments, "../../data/processed/gold_standard/annotation_comments.csv", row.names = FALSE)
```


# Rearrange columns
```{r}
annotations <- annotations %>%
  select(-contains("agreement")) %>%
  select(
    merge_id,
    report_name,
    starts_with("llm"),
    starts_with("non_exp"),
    starts_with("exp_group"),
    starts_with("exp_disc"),
  )
```

# Split report_name 
split report_name into company name and report year
```{r}
annotations <- annotations %>%
  separate(
  report_name, c("company_name", "report_year", "suffix"), sep = "_", remove = FALSE) %>%
  select(-report_name, -suffix)
```

Correct discrepancy between report_name and company_name for "vital energy" to "uniper"
```{r}
annotations <- annotations %>%
  mutate(company_name = ifelse(grepl("vital energy", company_name), "uniper", company_name))
```

# Remove duplicates and arrange by report_name, year, scope, page
```{r}
annotations <- annotations %>% distinct() %>% arrange(company_name, report_year, llm_scope, llm_year)
```

# Save dataset
```{r}
write.csv(annotations, "../../data/processed/gold_standard/annotation_dataset.csv", row.names = FALSE)
```