---
title: "unit_normalization.Rmd"
author: "Anna Steinberg"
date: "`r Sys.Date()`"
output: distill::distill_article
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Goal: Create dictionary for unit and value normalization from exploring the differences in the annotations

```{r}
library(tidyverse)
```

Read cleaned data
```{r}
df <- read.csv("../data/processed/non_expert_annotations/non_expert_annotations_cleaned.csv")
```

### Inspect unit column

```{r}
llm_units <- df %>% select(llm_unit) %>% distinct()
corrected_units <- df %>% select(corrected_unit) %>% distinct()
units <- llm_units %>% full_join(corrected_units, by = c("llm_unit" = "corrected_unit"))
```

Observations:
- numeric normalisation needed: e.g. 10^3 => 1000
- character normalisation, e.g. t-C02 => t C02, C02-e => C02 e, kt CO₂ eq => kt CO2 e
- word normalisation, e.g. carbon dioxide => CO2; Metric/metric tons, tonnes, Tonnes => t; MT of CO2 e => MT CO2 e; thousand or in thousand => k, equivalents => e
- MT can represent Megatonne or Metric tons ==> cannot unify
- Aссording to https://en.wikipedia.org/wiki/Ton US tons are not the same as tonnes or metric tons. We only unify tonnes and metric tons and leave tons as is.

Our goal is to normalize the units so that we get the following variations:
- t CO2, t CO2e, kt CO2, kt CO2e, mt CO2, mt CO2e
- MT CO2e, MT CO2
- Kg CO2e

Map all variations to a common entry
```{r}
# We first define the potential diverse patterns for the different components of unit which should be mapped to one common entry
tons_str <- c("tonnes", "tonne", "Tonnes", "Tonne", "metric ton", "Metric ton", "Metric tons", "metric tons", "metric tonnes", "Metric tonnes", "metric t")
ton_pattern <- paste0("\\b(", paste(tons_str, collapse = "|"), ")\\b")

k_str <- c("10\\^3", "^thousand", "1,000", "1’000", "^Thousands")
k_pattern <- paste0("\\b(", paste(k_str, collapse = "|"), ")\\b")

kt_str <- c("kilotonnes", "metric kilotons", "kilotonne", "metric kiloton")
kt_pattern <- paste0("\\b(", paste(kt_str, collapse = "|"), ")\\b")

co2_str <- c("CO 2", "CO₂", "carbon dioxide", "C02")
co2_pattern <- paste0("(", paste(co2_str, collapse = "|"), ")")

eq_str <- c("equivalents?", "eqv", "eq\\.?")
eq_pattern <- paste0("(", paste(eq_str, collapse = "|"), ")")

# We search for the patterns and replace by common normalized entry
units <- units %>% mutate(normalized = llm_unit,
    normalized = str_replace_all(normalized, regex(ton_pattern, ignore_case = TRUE), "t"),
    normalized = str_replace_all(normalized, regex(k_pattern, ignore_case = TRUE), "k"),
    normalized = str_replace_all(normalized, regex(kt_pattern, ignore_case = TRUE), "kt"),
    normalized = str_replace_all(normalized, regex(co2_pattern, ignore_case = TRUE), "CO2"),
    normalized = str_replace_all(normalized, regex(eq_pattern, ignore_case = TRUE), "e"),
    normalized = str_replace_all(normalized, fixed("of"), ""), 
    normalized = str_replace_all(normalized, fixed(" emissions"), ""),
    normalized = str_replace_all(normalized, fixed(" (t) "), ""),
    normalized = str_replace_all(normalized, fixed(" (CO2e)"), ""),
    normalized = str_replace_all(normalized, fixed("t CO2 e in thousands"), "kt CO2e"),
    
)


```

Remove space between "k" and "t", "CO2" and "e" and include space after "t" and "kt"
```{r}

units <- units %>% mutate(normalized = str_replace_all(normalized, "k t", "kt"),
                          normalized = str_replace_all(normalized, regex("(CO2 e|CO2-e)"), "CO2e"),
                          normalized = str_replace_all(normalized, regex("(-CO2|  CO2)"), " CO2"),
                          normalized = str_replace_all(normalized, regex("ktCO2e", ignore_case = TRUE), "kt CO2e"),
                          normalized = str_replace_all(normalized, regex("(MTCO2e|MT  CO2e)"), "MT CO2e"),
                          normalized = str_replace_all(normalized, regex("(tCO2e|t  CO2e)"), "t CO2e"),
                          normalized = str_replace_all(normalized, "Kg", "kg"),
                          normalized = str_replace_all(normalized, "Kt", "kt"))


```

How many distinct versions of units are there?

```{r}
units %>% select(normalized) %>% distinct()
```

Create dictionary for unit normalization
```{r}
unit_dict <- units %>% select(llm_unit, normalized) %>% distinct() %>% rename(unit = llm_unit, normalized_unit = normalized)
```

Save dictionary to use when comparing llm and human annotated values
```{r}
write.csv(unit_dict, "../data/processed/unit_normalization.csv", row.names = FALSE)
```

