---
title: "non_expert_annotations_data_wrangling"
author: "Anna Steinberg"
date: "2024-12-09"
output: html_document
---

# Goal of script: Read every non-expert annotation file in a folder, extract metadata, and append all data into a single csv file

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Load libraries
```{r}
library(readxl)
library(tidyverse)
library(purrr)
library(fs)
```

# Define the function to read and process one file
```{r}
# Function to process each file
read_process_file <- function(file_path) {
  print(file_path)
  # Load the metadata rows
  metadata_df <- read_excel(file_path, sheet = 1, range = cell_rows(1:8), col_names = FALSE, col_types = rep("text", 15))[1:4]
  
  # Pivot the metadata rows to a single row
  metadata_df <- metadata_df %>% select(1,4) %>%
    rename( "Variable" = 1, "Entry" = 2) %>% pivot_wider(names_from = Variable, values_from = Entry) %>%
    mutate(`Annotator ID:` = as.numeric(`Annotator ID:`))
  
  # Set column_types to guarantee consistent loading of columns
  column_types <- c("text", "text", "text", "numeric", "numeric", "text", rep("text", 19))
  
  # Load the main data, assuming the data starts after the metadata rows
  data_df <- read_excel(file_path, skip = 8, col_types = column_types)
  
  # Combine with metadata
  data_df <- bind_cols(data_df, metadata_df)
  
  # Remove rows without a row ID (assuming 'ID' is the first column after the header)
  data_df <- data_df %>% filter(!is.na(ID))
  
  return(data_df)
}
```

To test function: uncomment following line
```{r}
#read_process_file("../../data/raw/non_expert_annotations/acuity brands inc_2022_report_1.xlsx")
```


# Define function which loops through all files, reads data, concatenates and saves as csv
````{r}
process_excel_files <- function(folder_path, output_file_name) {
  # Get all file names in the directory, filter out hidden files
  file_paths <- fs::dir_ls(folder_path, type = "file")

  # Map the read_process_file function (defined above) over all file paths, read and process each file
  all_dataframes <- map_df(file_paths, read_process_file)
  
  # Remove unnecessary columns
  all_dataframes <- all_dataframes %>% select(-c(34:40))
  
  # Determine the parent directory of the specified folder
  parent_dir <- str_replace(folder_path, "raw", "processed")
  fs::dir_create(parent_dir)  # Ensure directory exists
  
  # Construct the full path for the output file in the parent directory
  output_file_path <- file.path(parent_dir, output_file_name)
  
  # Save the concatenated dataframe
  write.csv(all_dataframes, output_file_path, row.names = FALSE)
  
  return(all_dataframes)
}
```

# Run the function to process all files in the specified folder
```{r}
folder_path <- "../../data/raw/non_expert_annotations/"
output_file_name <- "non_expert_annotations_raw.csv"
concatenated_df <- process_excel_files(folder_path, output_file_name)
```

