---
title: "03_non_expert_annotations_data_checks"
author: "Anna Steinberg"
date: "`r Sys.Date()`"
output: distill::distill_article
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

### Load packages

```{r message=FALSE, warning=FALSE}
library(tidyverse)
```


### Load data
```{r}
df <- read.csv("../../data/processed/non_expert_annotations/non_expert_annotations_cleaned.csv")
```

## Data quality checks

1.  Does a report have more than 100 or less than 80 rows? (we expect at least 80 rows per report due to 2 annotators * 4 scopes * 10 years = 80)

```{r}
df %>% group_by(report_name) %>% summarise(rows = n()) %>%
  filter(rows < 80 | rows > 100) %>%
  arrange(rows)
```

Manual inspection: in jetblue airways corp_2019_report.pdf LLM and annotators added a lot of rows. No annotation or processing error, no need to correct it.

2.  Is report name, pages_searched, annotator ID or any of the doc level info missing? We expect no Missings.

```{r}
df %>% filter(is.na(report_name) | is.na(pages_searched) | is.na(annotator_ID))
```

3.  Did only one or both annotators add rows manually? If the annotation convention is clearly enough defined, we would expect both annotators to add rows manually. 

```{r}
df %>% group_by(ID, report_name) %>% 
  filter(str_starts(ID, "x")) %>%
  summarise(distinct_annotators = n_distinct(annotator_ID)) %>%
  arrange(desc(distinct_annotators))
```
However, only three records were added by both annotators. So annotation convention needs to be refined.

4.  Does "expert adjudication needed" column contain missing values? It was mandatory for non-experts to provide an answer here. 

```{r}
df %>% filter(is.na(record_expert_needed) | is.na(document_expert_needed)) %>% group_by(annotator_ID) %>% summarise(nrows = n())
```

5.  Are there any discrepancies between x_correct and corrected_x for x = value, unit, page? If x_correct == "Yes" | NA the corrected_x column should always be NA. If it is already correct, correction is not needed.

```{r}
df %>% filter((value_correct == "Yes" | is.na(value_correct)) & !is.na(corrected_value))
```

```{r}
df %>% filter((unit_correct == "Yes" | is.na(unit_correct)) & !is.na(corrected_unit))
```

```{r}
df %>% filter((page_correct == "Yes" | is.na(page_correct)) & !is.na(corrected_page))
```
